article title

### 2022-07-19 article.tex
Refactor links using hyperref, hypersetup

% very useful for hyperlinks
\usepackage[unicode]{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=blue
}

% useful for Greek letters in text mode
\usepackage[cbgreek]{textgreek}

% required for bibtex URLs
\usepackage{url}

@@

@@

\section{URLs}
\label{sec:urls}
Hyperlinks within the document can be easily added. For example, see Graphics \ref{sec:graphics} and Anatomy of a matplotlib figure \ref{fig:anatomy_of_a_matplotlib_figure} and Definition of a limit \ref{def:limit}.

@@

\newpage
\section{To do}

\begin{itemize}
    \item list to do items here
\end{itemize}

>>>>

% very useful for hyperlinks
% useful for Greek letters in text mode
\usepackage[cbgreek]{textgreek}

@@

\usepackage[unicode]{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=magenta,
    citecolor=green,
    linkcolor=red
}

@@

\section{URLs}
\label{sec:urls}
Hyperlinks within the document can be easily added. For example, \hyperref[sec:graphics]{see Graphics} and \hyperref[fig:anatomy_of_a_matplotlib_figure]{Anatomy of a matplotlib figure} and \hyperref[def:limit]{Definition of a limit}.

@@
